Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2022-04-07 analysis/paper/London_HauloutBeahvior.Rmd

@@

>>>>

  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}

@@

\blandscape
# Supplemental Material {-}

# S1. Supplemental Table of Bio-logger Deployment Details

The following table provides additional details about the timing, location, and
agencies responsible for the bio-logger deployments used in this study.

```{r, include=TRUE}
library(gt)
library(googlesheets4)
library(glue)

deploy_tbl <- read_sheet("1MpCiyAKWLBXufwnzW8QTnb2SsTkrKSuPlWdpWMnqoto")

deploy_tbl %>% 
  dplyr::select(species, agency, deploy_year, permit, location, speno, sex, age, publications) %>% 
  dplyr::group_by(species, agency, deploy_year, location, publications) %>% 
  dplyr::mutate(agency = 
                  case_when(
                    agency %in% c('ADFG') ~ "Alaska Dept. Fish & Game",
                    agency %in% c('NSB') ~ "North Slope Burough",
                    agency %in% c('PEP') ~ "NOAA Alaska Fisheries Sci. Ctr",
                    agency %in% c('NPWC') ~ "N. Pacific Wildlife Consortium"
                  )) %>% 
  dplyr::summarise(permits = toString(unique(permit)),
                   n_seals = n(),
                   sex = toString(unique(sex)),
                   age_class = tolower(toString(unique(age)))) %>% 
  dplyr::arrange(species, agency, deploy_year) %>% 
  gt(
    rowname_col = "species",
    groupname_col = "agency"
  ) %>% 
  cols_label(
    deploy_year = "Year Deployed",
    location = "Location",
    publications = "Publication(s)",
    permits = "Permits",
    n_seals = "No. Seals",
    sex = "Sex",
    age_class = "Age Class"
  ) %>% 
  tab_style(
    style = list(
      cell_text(style = "italic")
    ),
    locations = cells_body(
      columns = publications
    )
  ) %>% 
  cols_align(
    align = "center",
    columns = everything()
  ) %>% 
  cols_align(
    align = "right",
    columns = age_class
  ) %>% 
  tab_header(
    title = "Data Contributions From Collaborators and Additional Deployment Details"
  )

```
\elandscape
